---
title: "Communicating between R and WebVR sessions"
author: "Miles McBain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Communicating between R and WebVR sessions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A live connection between an R session and a running scene being served by
`r2vr` is supported using a websocket API. This allows novel usage scenarios including:
* An 'operator' triggering events for a scene viewer using the R console 
  - Alternately using controls laid out in a html widget or shiny app.
* Streaming of data from R to VR scenes could be used create animations or
  dynamic visualisations

The communication layer is full duplex, meaning it is possible for events
triggered in VR to be relayed to the R session, although the API for setting up
handlers for asynchronous events arriving from VR will not be discussed in
this vignette in this release. This will be deferred until a suitable usecase is
found (Feel free to open a GitHub issue if you find yourself wanting to do this
and we can discuss).

# Elements of R-VR communication

## Websocket enabled r2vr server
The communication layer is enabled by creating scene object using `a_scene()`
with the `.websocket = TRUE` argument. This will cause each user browser session
to open a websocket connection with the `r2vr` server as part of the scene
rendering process.

A websocket enabled `r2vr` server can broadcast messages to connected users
that can trigger updates in their VR scenes. This is done by calling the
`send_messgages()` method of the server.

## `send_messages()`
This method takes a message or list of messages to be broadcast to all connected scenes.
Messages are created using the `r2vr` functions:

* `a_event()` - used to inject A-Frame events into the scene. This can be any
  kind of event including those normally driven by user interaction: like
  'fusing' or 'click'. The scene will emit the event defined by this call on the
  entity identified by `id`. See documenation for more details.
* `a_update()` - used to modify the component configuration of entities in the
  scene. It is possible to attach a new component or, replace component
  attributes either fully or partially.
* `a_remove_component()` - used to remove a `component` from an entity identified by `id`.
* `a_remove_entity()` - used to remove an entity identified by `id` from a
  scene. Child entities are also removed.

Adding an entity to a VR scene dynamically from R is not supported at the moment
although will be in the future.

# Examples

## A console controlled 360 image slide show

For this example we'll add some 360 photos to a scene and allow them to be
stepped through by a console operator.

The images are hosted in an external GitHub repository:
https://github.com/MilesMcBain/360_image_examples. The code below reads them
directly from there.

### Scene setup

The following code creates asset objects from a list of supplied URLs, and then
sets up a scene containing a 'sky' sphere entity, `canvas_360`, that we can set
the internal texture of using its `src` component. The internal texture is
initially set to the first of the images.

```{r eval = FALSE}
library(r2vr)
library(purrr)

img_urls <-  c("https://ucarecdn.com/6cce6743-cfaa-4258-a93b-240e912c1ecc/",
               "https://ucarecdn.com/f2595d03-1a21-4ef8-9c07-6ef9a4972be7/",
               "https://ucarecdn.com/2f5030e8-a3c0-4045-ad84-a96ea25dfab0/",
               "https://ucarecdn.com/ef0090e4-703e-4edd-9527-42853eed9cfb/")

img_ids <- paste0("360img", seq(length(img_urls)))

img_assets <- map2(img_ids, img_urls, ~a_asset(id = .x,
                                               src = .y,
                                               tag = "img"))

canvas_360 <- a_entity(.tag = "sky",
                       id = "canvas360",
                       position = c(0, 0, 0),
                       src = img_assets[[1]], ## src is the inital texture asset
                       .assets = img_assets   ## these are the assets we will change to
                       )

the_scene <- a_scene(.title = "A 360 image slideshow",
                     .template = "empty",
                     .children = list(canvas_360),
                     .websocket = TRUE) ## Enable coms with R server

the_scene$serve()
```

The images in this scene have a combined size of about ~25mb, so the scene will
need some time to load.

### Control from R

With the scene running we now turn our attention to writing an 'advance()'
function that we can call to advance to the next image in the list.


```{r eval = FALSE}

img_index <- 1
n_images <- length(img_ids)

advance <- function(){
    img_index <<- ifelse(test = img_index == n_images,
                         yes = 1,
                         no = img_index + 1)

    the_scene$send_messages(a_update(id = "canvas360",
                                     component = "src",
                                     attributes = img_assets[[img_index]]$reference())
              )
    message("Now showing: ", img_assets[[img_index]]$id) 
  }

```

Calling `advance()` will trigger a transition to the next image. Within this
function, an update message is composed that is sent using the scene object. The
transition should occur instantly since all assets are loaded prior to the scene
being shown. 

One trick here is that we called the `reference()` method of an
a_asset to get the text to used in the `src` attribute. The transition should
occur instantly since all assets are loaded prior to the scene being shown.

## Streaming Position Data to VR

In this scene we're going to look at streaming sea level height from R to a
scene containing an island. First we'll look at sending information interactively
using the R REPL in a similar way to the prevoius example.

```{r, eval = FALSE}
library(r2vr)

island_model <- a_asset(id = "island",
                        src = "https://cdn.glitch.com/7cadb230-57b2-4aae-9de9-e60de097035e%2Fisland.gltf?1510323826393")

island <- a_entity(gltf_model = island_model,
                   scale = c(0.5, 0.5, 0.5),
                   position = c(0, 2, 0))

water <- a_entity(id = "water",
                  .tag = "box",
                  width = 30,
                  depth = 30,
                  height = 5,
                  material = list(color = "#42B9F4",
                               opacity = 0.5,
                               transparent = TRUE,
                               shader = "flat"
                               )
                  )

the_scene <- a_scene(.children = list(island, water),
                     .websocket = TRUE)

the_scene$serve()


sea_level <- function(level){
  level <- level - 2
  the_scene$send_messages(
              a_update(id ="water",
                       component = "position",
                       attributes = list(x = 0, y = level, z = 0))
            )
}

```

With the scene open in the browser, the this `sea_level()` funciton you can set
the height of the water for a viewer of the VR visualisation. We'll create a
simple shiny app that can control the water with a slider.

```{r, eval = FALSE}
library(shiny)

ui <- flowLayout(
  sliderInput("level", "Set the sea level", 
              min = -2, max = 4, step = 0.1, round = FALSE)
)

onStart <- function(){
  ## Setup VR Scene
  island_model <- a_asset(id = "island",
                          src = "https://cdn.glitch.com/7cadb230-57b2-4aae-9de9-e60de097035e%2Fisland.gltf?1510323826393")

  island <- a_entity(gltf_model = island_model,
                     scale = c(0.5, 0.5, 0.5),
                     position = c(0, 2, 0))

  water <- a_entity(id = "water",
                    .tag = "box",
                    width = 30,
                    depth = 30,
                    height = 5,
                    material = list(color = "#42B9F4",
                                    opacity = 0.5,
                                    transparent = TRUE,
                                    shader = "flat"
                                    )
                    )
  ## need to use global assign to make it visible to server
  the_scene <<- a_scene(.children = list(island, water),
                       .websocket = TRUE)
  the_scene$serve()
}

server <- function(input, output){

  ## Setup response to silder
  slider_value <-
    observeEvent(input$level,
    {
      update_message <- a_update(id ="water",
                          component = "position",
                          attributes = list(x = 0,
                                            y = input$level - 2,
                                            z = 0))

      the_scene$send_messages(update_message)
    }
    )
}

  runApp(shinyApp(ui,server, onStart), launch.browser = TRUE)

a_kill_all_scenes()
```
The VR app needs to be embedded inside the shiny app since the Shiny event loop takes over the R process. However care must be taken to only start it once, which is why it is in the onStart function. Correpsondlingly it would go in global.R for a directory based app.
