---
title: "Making a VR Scatterplot"
author: "Miles McBain"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Making a VR Scatterplot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Making VR Scatteplots

This document describes two methods of using `r2vr` to create a VR scatter plot:
1. Using a single entity that with a community developed A-Frame scatterplot component attached.
2. Generating a list of entity HTML elements representing the geometric primitives of the plot data and dressing.

## Using a community component

Rather than building a plot from A-Frame primitives, it's a good idea to check
if there is some A-Frame components written in Javascript that will suit the
objective. Places to look are:
* [The A-Frame component registry](https://aframe.io/aframe-registry/)
* [The NPM archive 'aframe' tag](https://www.npmjs.com/search?q=aframe)

As it happens there are a couple of options for making VR plots. This example
will use: https://github.com/zcanter/aframe-scatterplot.

According to the documentation our data needs to
be JSON that looks like this:

```{js, eval = FALSE}
[
 {
   // Data Point
   "Field1": 13.90738679789567,
   "Field2": 11.77935227940546,
   "Field3": 12.02052097080796,
   "Field4": 11.31274091176219,
   "Field5": 14.13415151546462,
 },
 {
   // Data Point
   "Field1": 12.29829187876160,
   "Field2": 10.12398967761787,
   "Field3": 16.81298749861520,
   "Field4": 13.92371645984898,
   "Field5": 11.35138647618786,
 },
 {...},
 {...},
 ]
```

```{r}
library(r2vr)
library(jsonlite)
library(ggplot2)

a_scatterplot <- function(json_data, x, y, z, ...){

  ## js sources for scatterplot
  .scatter_source <- "https://cdn.rawgit.com/zcanter/aframe-scatterplot/master/dist/a-scatterplot.min.js"
    .d3_source <- "https://cdnjs.cloudflare.com/ajax/libs/d3/4.4.1/d3.min.js"

  ## Create in-memory asset for JSON data
  ## A regular a_asset could be used that points to a real file
  ## this is necessary in a vignette to avoid CRAN issues.
  json_file_asset <- a_in_mem_asset(id = "scatterdata",
                                    src = "./scatter_data.json",
                                    .data = json_data)

  a_entity(.tag = "scatterplot",
           src = json_file_asset,
           .js_sources = list(.scatter_source, .d3_source),
           x = x,
           y = z,
           z = z, ...)
}

diamonds_json <- jsonlite::toJSON(diamonds) 

my_scene <- a_scene(.template = "empty",
                    .children = list(
                      a_scatterplot(diamonds_json, x = "depth", y = "carat", z = "table",
                                    val = "price",
                                    xlabel = "depth", ylabel = "carat", zlabel = "table",
                                    showFloor = TRUE,
                                    ycage = TRUE,
                                    title = "Price of Diamond$$$",
                                    pointsize = "10",
                                    position = c(0, 0, -2),
                                    scale = c(3,3,3)),
                    a_pc_control_camera()))

my_scene$serve()
my_scene$stop()
```

## A Scattleplot from scratch using HTML entities

This section contains `r2vr` code to compose a simple 3D scatter plot of `mpg`
vs `wt` vs `hp`, coloured by `am` from the `mtcars` data. Since it is made 'from
scratch', using geometric primitives, there are a few considerations: What
dimensions should the plot be? How do we scale the data to these dimensions? Can
we apply labels that appear when the points are looked at?

Since data is used to answer these questions, we may as well
create a function that returns a scene so we can re-use the code.

The code here should be considered a proof of concept only. It is overly long
and could be decoupled and abstracted further into composable functions on the way to creating
a general purpose VR plotting API. At the moment that API is not planned for
`r2vr`. If it comes, it will be as a separate package that builds on `r2vr`.

```{r}
library(r2vr)
library(purrr)
library(tibble)

a_scatter_ents <- function(x, y, z, colour = rep(1, length(x)), palette_fn = rainbow, sizes = rep(0.1, length(x)), labels, dimensions = c(2,2,2), ...){

  force(sizes)
  x_label <-  deparse(substitute(x))
  y_label <-  deparse(substitute(y))
  z_label <-  deparse(substitute(z))
  legend_label <- deparse(substitute(colour))

  colour_factor <- as.factor(colour)
  ent_colours <- palette_fn(nlevels(colour_factor))[colour_factor]

  range_scale <- function(a) (a - min(a, na.rm=TRUE)) / diff(range(a, na.rm=TRUE))
  x <- range_scale(x)
  y <- range_scale(y)
  z <- range_scale(z)

  positions <- cbind(x,y,z) * dimensions

  entity_data <-
    tibble::tibble(position = purrr::transpose(as.data.frame(positions)),
                       color = ent_colours,
                       radius = sizes,
                   label = labels)

  points <-
    purrr::pmap(entity_data, function(position, color, radius, label){

    id = gsub(" ", "", label)
    point <- a_entity(.tag = "sphere", position = unlist(position), color = color,
                      radius = radius,
                      event_set__click =
                        list(`_event`= "click",
                             `_target`= "#labelview",
                             visible = TRUE,
                             value = label),
                      event_set__leave =
                        list(`_event`="mouseleave",
                             `_target`= "#labelview",
                             visible = FALSE,
                             value = label),
                      .js_sources = "https://unpkg.com/aframe-event-set-component@^4.0.0/dist/aframe-event-set-component.min.js")
    point
  })

  ## camera entity with cursor
  cursor <- a_entity(.tag = "camera", position = c(0,1.6,3),
                     .children = list(
                       a_entity(.tag = "cursor", position = c(0,0,3)),
                       a_label(id = "labelview",
                               text = "",
                               scale = c(0.4, 0.4, 0.4),
                               position = c(0,-0.4,-1))))
  ## make axis labels
  label_offset <- 0.1 * dimensions

  x_axis_label <- a_label(text = x_label,
                          position = dimensions * c(0.5, 0.1, 0))

  y_axis_label <- a_label(text = y_label,
                          position = dimensions * c(0, 0.5, 0),
                          rotation = c(0, 45, 0))

  z_axis_label <- a_label(text = z_label,
                          position = dimensions * c(0, 0.1, 0.5),
                          rotation = c(0, 90, 0))


  ## make each axis
  x_axis <- a_entity(line = list(start = c(0,0,0),
                                 end = c(dimensions[[1]], 0, 0),
                                 color = "#000000"),
                     children = list(x_axis_label))
  y_axis <- a_entity(line = list(start = c(0,0,0),
                                 end = c(0, dimensions[[2]], 0),
                                 color = "#000000"),
                     children = list(y_axis_label))
  z_axis <- a_entity(line = list(start = c(0,0,0),
                                 end = c(0, 0, dimensions[[3]]),
                                 color = "#000000"),
                     children = list(z_axis_label))
  ## make legend
  legend_levels <- levels(colour_factor)
  legend_colours <- palette_fn(nlevels(colour_factor))
  if(length(legend_levels > 1)){
    box_size = 0.2
    box_spacing = 0.2
    legend_position = c(dimensions[[1]] * 1.1, 0, 0)
    legend_ents <- purrr::imap(legend_levels,
                function(level, index){
                  a_entity(.tag = "text", value = as.character(level),
                           position = c(0,
                                        index * (box_size + box_spacing), 0),
                           rotation = c(0, 0, 0),
                           color = "#000000",
                           align = "right",
                           anchor = "right",
                           text = list(xOffset = box_size*2),
                           geometry= list(primitive = "box",
                                          width = box_size,
                                          height = box_size,
                                          depth = box_size),
                           material = list(transparent = FALSE,
                                           color = legend_colours[[index]] )
                           )
                })

    ## Legend label
    legend_label <- a_entity(.tag = "text", value = legend_label,
                             position = c(0, (box_size + box_spacing) *
                                                          (nlevels(colour_factor) + 1), 0),
                             rotation = c(0, 0, 0),
                             color = "#000000",
                             align = "center",
                             geometry= list(primitive = "box",
                                            width = box_size,
                                            height = box_size,
                                            depth = box_size),
                             material = list(transparent = TRUE,
                                             opacity = 0))
    plot_legend <- a_entity(position = legend_position,
                            .children = c(legend_ents, legend_label))
  } else {
    plot_legend <- list()
  }

  ## make plot and add points
  plot <- a_entity(position = c(0,0.1,-3),  .children = c(x_axis, y_axis,
                                                         z_axis, points,
                                                         plot_legend))

  my_scene <- a_scene(.template = "basic",
                      .title = "A scattering of cars",
                      .children = c(cursor, plot))

  my_scene
}

my_scene <- a_scatter_ents(
  x = mtcars$hp,
  y = mtcars$mpg,
  z = mtcars$wt,
  colour = mtcars$am,
  purrr::partial(rainbow, alpha = NULL), #for RGB -alpha
  labels = row.names(mtcars),
  dimensions = c(3,3,3))


## my_scene$serve()
## my_scene$stop()
```


## Local Variables:
## ess-r-package--project-cache: (r2vr . "/home/miles/repos/r2vr/")
## End:
