---
title: "Communicating between R and WebVR sessions"
author: "Miles McBain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

A live connection between an R session and a running scene being served by
`r2vr` is supported using a websocket API. This allows novel usage scenarios including:
* An 'operator' triggering events for a scene viewer using the R console 
  - Alternately using controls laid out in a html widget or shiny app.
* Streaming of data from R to VR scenes could be used create animations or
  dynamic visualisations

The communication layer is full duplex, meaning it is possible for events
triggered in VR to be relayed to the R session. When the websocket API is
enabled, the `scene` element has an event handler attached for events of type 'r_server_message'. 'r_server_message' events are passed to the R server.

Ideally the onmessage handler would route the message to an entity based on id, or the top level scene.

# Examples

## A console controlled 360 image slide show

For this example we'll add some 360 photos to a scene and allow them to be stepped through by a console operator.

The images are hosted in an external GitHub repository: https://github.com/MilesMcBain/360_image_examples. The code below reads them directly from there.

### Scene setup

The following code creates asset objects from a list of supplied URLs, and then
sets up a scene containing a 'sky' sphere entity, `canvas_360`, that we can set
the internal texture of using its `src` component. The internal texture is
initially set to the first of the images.

```{r}
library(r2vr)
library(purrr)

img_urls <- c("https://cdn.rawgit.com/MilesMcBain/360_image_examples/3f9478cba6db12b425398102ab8d18e0a471f811/SAM_100_0382.jpg",
              "https://cdn.rawgit.com/MilesMcBain/360_image_examples/3f9478cba6db12b425398102ab8d18e0a471f811/SAM_100_0384.jpg",
              "https://cdn.rawgit.com/MilesMcBain/360_image_examples/3f9478cba6db12b425398102ab8d18e0a471f811/SAM_100_0385.jpg",
              "https://cdn.rawgit.com/MilesMcBain/360_image_examples/3f9478cba6db12b425398102ab8d18e0a471f811/SAM_100_0387.jpg")

img_ids <- paste0("360img", seq(length(img_urls)))

img_assets <- map2(img_ids, img_urls, ~a_asset(id = .x,
                                               src = .y,
                                               tag = "img"))

canvas_360 <- a_entity(tag = "sky",
                       id = "canvas360",
                       position = c(0, 0, 0),
                       src = img_assets[[1]]
                       )

the_scene <- a_scene(title = "A 360 image slideshow",
                     template = "empty",
                     children = list(canvas_360),
                     websocket = TRUE) ## Enable coms with R server

the_scene$serve()
```

### Control from R
With the scene running we now turn our attention to writing an 'advance()' function that we can call to advance to the next image in the list.

```{r}

img_index <- 2
n_images <- length(img_ids)

advance <- function(){
    current_index <- img_index
    img_index <<- ifelse(test = img_index == n_images,
                         yes = 1,
                         no = img_index + 1)

    the_scene$send_messages(list(
                a_update(id = "canvas360",
                         component = "src",
                         attributes = img_assets[[current_index]]$reference())
              ))
    message("Now showing: ", img_assets[[current_index]]) 
  }

```

## Streaming particle positions

## Notifications from VR

## Old
```{r}
library(r2vr)

sources <- a_entity(js_sources = c("https://unpkg.com/aframe-event-set-component@^4.0.0/dist/aframe-event-set-component.min.js") )

box <- a_entity("box", id = "block",
                position = c(0, 1, -4),
                material = list(color = "red"),
                event_set__1 = list(`_event` = "switch_colour", material.color = "blue"),
                event_set__2 = list(`_event` = "rotate", rotation = c(0, 45, 0)))

my_scene <- a_scene(template = "basic",
                    children = list(box, sources),
                    websocket = TRUE)

my_scene$serve()

test_event <- list(a_event(id = "block",
                           event_name = "switch_colour",
                           event_detail = "any",
                           bubbles = FALSE),
                   a_event(id = "block",
                           event_name = "rotate",
                           event_detail = "any",
                           bubbles = FALSE)
                   )

my_scene$send_messages(test_event)

test_update <- list(a_update(id = "block",
                             component = "position",
                             attributes = list(x = 0, y = 0, z = -4)),
                    a_update(id = "block",
                             component = "color",
                             attributes = "green"))

my_scene$send_messages(test_update)

#try adding own handlers
my_scene$attach_ws_msg_hook(function(message, id){
  print(id)
  print(message)
})

a_kill_all_scenes()

```


