---
title: "Coral Cover (3D Testing)"
author: "Jon Peppinck"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_width: 7
fig_height: 3
vignette: >
  %\VignetteIndexEntry{Coral Cover (3D Testing)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
  knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.height = 3,
  fig.width = 7
  )
require(knitr)
```
  
# Annotate 3D Virtual Reality Images by Creating an Interactive WebVR scene

`r2vr` has been extended to be able to help train users to annotate virtual reality images more accurately. The 3D Testing will randomly select `3` images from a pool of images. Users are able to annotate selected markers (for each image) as either `C` or `N` to classify the bounded region as either containing mostly `Coral` or `Not Coral` respectively. The user will also be prompted to answer evaluation questions. The data generated from the 3d training and 3d testing can be read into R for analysis.

## Case Study: Coral Cover

```{r}
library(r2vr)

IPv4_ADDRESS <- find_IP() # Note: If not on Windows, enter IP directly

## TODO: SET full name here
# set_user("Firstname-Lastname") # default to be overridden
set_user("Jon-Peppinck")

## OPTIONAL: '?set_marker_and_props' shows configuration options
# i.e. Number of markers and size of markers, but keep "3d"
set_marker_and_props("3d") 

## OPTIONAL: '?set_colors'
set_colors()

R2VR_CDN <- "https://cdn.jsdelivr.net/gh/ACEMS/r2vr@experiment" # NOTE: Subject to change

R2VR_3D_IMAGES <- paste0(R2VR_CDN, "/inst/ext/images/3d/")

# TODO: Select images
# NOTE: If have other local images on PC can change img_paths to be a vector of relative file location for the current working directory
img_paths <- paste0(
  R2VR_3D_IMAGES,
  c("100030039.jpg",
    "120261897.jpg",
    "130030287.jpg",
    "130050093.jpg")
)

img_paths_and_points <- list(
  # 3D image paths
  list(img = img_paths[1]),
  list(img = img_paths[2]),
  list(img = img_paths[3]),
  list(img = img_paths[4])
)

set_random_images(img_paths_and_points)

## TODO: SET evaluation question and responses here
evaluation_questions <- list(
  list(question = "Did you enjoy this experiment?", answerOne = "Very much", answerTwo = "Yes", answerThree = "A little", answerFour = "No"),
  list(question = "On a scale of 1-4, how would you rate your experience?", answerOne = "1", answerTwo = "2", answerThree = "3", answerFour = "4")
)

## OPTIONAL: '?set_questions_and_responses'
set_questions_and_responses(evaluation_questions)

animals <- shared_setup_scene("3d", "testing") # DON'T CHANGE
```

## COMMANDS - 3D Testing

```{r}
start()
randomize_markers()
go_to()
go_to()
ask_question(1)
ask_question(2)
end()
testing_3d.df <- read("https://r2vr.herokuapp.com/api/3d/testing")
evaluation_3d.df <- read("https://r2vr.herokuapp.com/api/3d/evaluation")
rm(list=ls())
```
