---
title: "Making a VR Scatterplot"
author: "Miles McBain"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This document describes two methods of using `r2vr` to create a VR scatter plot:
1. Generating a list of entity HTML elements, one for every data point.
2. Using a single entity that with a community developed A-Frame scatterplot component attached.


## Generating HTML entities
We're going to make a simple 3D scatter plot of `mpg` vs `wt` vs `hp`, coloured by `am` from the `mtcars` data. It will be made from scratch using `r2vr` so there's a few considerations:
What dimensions should the plot be? How do we scale the data to these dimensions? Can we apply labels that appear when the points are looked at?

Since we're going to be using the data to answer these questions we may as well create a function that returns a list of entities so we can re-use the code.

```{r}

a_scatter_ents <- function(x, y, z, colours, sizes = rep(seq_along(x), 0.1), labels, dimensions = c(2,2,2), ...){
  x = mtcars$hp
  y = mtcars$wt
  z = mtcars$mpg
  colours = pals::cols25(2)[as.factor(mtcars$am)]
  sizes = rep(0.1,length(x))
  labels = row.names(mtcars)
  dimensions = c(2,2,2)

  range_scale <- function(a) (a - min(a, na.rm=TRUE)) / diff(range(a, na.rm=TRUE))
  x <- range_scale(x)
  y <- range_scale(y)
  z <- range_scale(z)

  positions <- cbind(x,y,z) * dimensions

  entity_data <-
    tibble::data_frame(position = purrr::transpose(as.data.frame(positions)),
                       color = colours,
                       radius = sizes,
                       label = labels)

  #purrr::pmap()

}

```

## Using a community component



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
